DEBS Grand Challenge: A High-Throughput, Scalable Solution for Calculating Frequent Routes and Profitability of New York Taxis

### 2015-05-13 presentation/grand_challenge.tex
modify the presentation

\author{Amila Suriarachchi} % Your name
\institute[CSU] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Colorado State University \\ % Your institution for the title page
\medskip
\textit{amilas@cs.colostate.edu} % Your email address
\medskip
}
\date{May 4, 2015} % Date, can be changed to a custom date

@@

\begin{figure}
        \includegraphics[width=0.8\linewidth]{DinamicHeap.png}
\end{figure}

@@

\footnotesize Initially throughput increases with the number of route process instances and comes to a steady state. For distributed setup latency comes to a steady state with higher process instances.

@@

\footnotesize Initially throughput increases with the number of route process instances and comes to a steady state. For distributed setup latency comes to a steady state with higher process instances.

>>>>

\author[Amila Suriarachchi]{Amila Suriarachchi \\ Shrideep Pallickara } % Your name
\institute[CSU] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Colorado State University \\ % Your institution for the title page
\medskip
\textit{amilas@cs.colostate.edu} % Your email address
\medskip
}
\date{\today} % Date, can be changed to a custom date

@@

\begin{figure}
        \includegraphics[width=0.7\linewidth]{DinamicHeap.png}
\end{figure}

@@

\footnotesize For distributed setup throughput increases up to 4 processors while latency remain in a constant after 5 processors. For single JVM setup throughput increases up to 2 nodes and slightly decreases with the number of processors while latency slightly increases with the number of processors.

@@

\footnotesize For distributed set up throughput linearly increases and latency increases with higher number of calculators. For single JVM set up throughput linearly increases up to 3 instances and latency slightly increases with the number of calculators.

\begin{frame}
\frametitle{Scalability with Window Size}

\begin{figure}
        \includegraphics[width=0.6\linewidth]{window.png}
\end{figure}

\footnotesize Both implementations scale even for 64h windows. DynamicHeap based algorithm performs better at higher window sizes.

\section{Conclusion}

\begin{frame}
\frametitle{Conclusion}
\begin{itemize}
        \item Our queries execute with O(log n) time complexity and hence scale with window size.
        \item Our partitioning technique can be used to scale up the system while producing the desired results. 
	\item We propose an algorithm to find the running median with O(log n) time complexity.
\end{itemize}
